FoRTE baseline

### 2019-04-18 analysis/paper/paper.Rmd
Add some paper notes about UMBS composition

- Secondary successional forest -- bigtooth aspen (_Populus grandidentata_), northern red oak (_Quercus rubra_), red maple (/Acer rubrum/), paper birch (_Betula papyrifera_), eastern white pine (_Pinus strobus_)
- Average age -- 95 years (2013)
- NEP in UMBS tower is 1.58 MG C ha-1 yr-1 (0.80-1.98) (1999-2006), but with landscape variation (REF?)
- Heavily logged in late 1800s and early 1900s, disturbed by fire until 1923
- Present day composition typical of upper Great Lakes region
- Previously, the site of the FASET experiment [@gough_2013_sustained; @gough_2008_multi]

>>>>

- Secondary successional forest -- bigtooth aspen (_Populus grandidentata_), northern red oak (_Quercus rubra_), red maple (/Acer rubrum/), paper birch (_Betula papyrifera_), eastern white pine (_Pinus strobus_)
- Average age -- 95 years (2013)
- NEP in UMBS tower is 1.58 MG C ha-1 yr-1 (0.80-1.98) (1999-2006), but with landscape variation (REF?)
- Heavily logged in late 1800s and early 1900s, disturbed by fire until 1923
- Present day composition typical of upper Great Lakes region
- Previously, the site of the FASET experiment [@gough_2013_sustained; @gough_2008_multi]
- UMBS is 87% upland and 13% wetland [@bergen_2007_observing]. We focus on the upland ecosystem, which has the following characteristics (from @bergen_2007_observing):
    - 20.4% moraine, 37.8% high outwash plain, 31.3% low outwash plain, 5.7% lake-margin terrace, 3.6% ice-contact, 1.2% lowland glacial lake
    - 60.9% aspen-dominated, 16.6% northern hardwood (/Acer saccharum/, /Acer rubrum/, /Fagus grandifolia/, /Tilia americana/ (basswood), /Betula alleghaniensis/ (yellow birch), /Fraxinus americana/ (white ash), /Tsuga canadensis/), 13.3% upland conifer (/Pinus strobus/, /Pinus resinosa/)
    - 1.6% northern red oak (/Quercus rubra/)
    - 60.9% transitioning from aspen to next succession, of which: 55.8% to northern hardwood, 34.7% to upland conifer, 3.8% to northern red oak, 2.6% to northern red oak-red maple, 3.1% to upland conifer-northern hardwood
